---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# iNZightRegression

<!-- badges: start -->
![R-CMD-check](https://github.com/iNZightVIT/iNZightRegression/workflows/R-CMD-check/badge.svg)
[![Coverage status](https://codecov.io/gh/iNZightVIT/iNZightRegression/branch/master/graph/badge.svg)](https://codecov.io/github/iNZightVIT/iNZightRegression?branch=master)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)
<!-- badges: end -->


An R package which provides summary information and plots which have been altered from those provided by base R.

It now handles `glm` object, as well as `svyglm` objects from the `survey` package.

## Installation

You can install the released version of iNZightRegression from [CRAN](https://CRAN.R-project.org) with:

``` r
# Not yet on CRAN - please use devtools below
# install.packages("iNZightRegression")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("iNZightVIT/iNZightRegression")
```

## Example

Plots and summaries of model objects:

```{r example, out.width = "50%", fig.align = "center"}
library(iNZightRegression)
iris.lm <- lm(Sepal.Width ~ Sepal.Length, data = iris)
inzplot(iris.lm, which = "residual")
inzplot(iris.lm, which = "scale")
inzplot(iris.lm, which = "leverage")
```
